### 2018-02-18 doc/manuscript.Rmd
reformat abstract
fix code from TG -> TAG

`r cite_f('tagfa')` shows the composition of each FA in the TG fraction (see 
`r cite_st('tagfa')` for a tabular presentation of the values). 
Three TGFA contributed `r aide::format_round(sum(tagfa$pct))`% to the total 
TG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r cite_f('heatmap')` shows a heatmap of the correlation of individual TGFA as
concentrations with the outcome variables and several basic characteristics.
As expected, nearly all TGFA had very strong positive correlations (r=
`r fa_cor$rng$TG[2]`) with clinically-measured TG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist[2]`). There were also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL[1]`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(HOMA2-%S: r=`r fa_cor$rng[['HOMA2-%S']][1]`, ISI: r=`r fa_cor$rng$ISI[1]`) than 
for the beta-cell function measures (all r<0.30). For correlations
of individual TGFA using mol% with the basic participant characteristics, as shown in 
`r cite_f('heatmap_mol')`, differences in correlations between fatty acids were
most evident for 14:0, 14:1n-7, 16:0, and 16:1n-7 that had a moderate positive
correlation with clinical TG (r=`r fa_cor_mol$rng$TG[1]`) while all other fatty
acids had a negative association (r=`r fa_cor_mol$rng$TG[2]`). In particular,
those fatty acids with the negative associations with clinical TG were all the
very long chain polyunsaturated fatty acids (e.g. 20:4n-6, 20:5n-3).
As seen in `r cite_f('heatmap_tagfa')`, four fatty acids (14:0,
16:0, 14:1n-7, and 16:1n-7) clustered together, each highly positively correlated
with each other and negatively correlated with all other fatty acids.

>>>>

`r cite_f('tagfa')` shows the composition of each FA in the TG fraction (see 
`r cite_st('tagfa')` for a tabular presentation of the values). 
Three TGFA contributed `r aide::format_round(sum(tagfa$pct))`% to the total 
TG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r cite_f('heatmap')` shows a heatmap of the correlation of individual TGFA as
concentrations with the outcome variables and several basic characteristics.
As expected, nearly all TGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG[2]`) with clinically-measured TG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist[2]`). There were also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL[1]`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(HOMA2-%S: r=`r fa_cor$rng[['HOMA2-%S']][1]`, ISI: r=`r fa_cor$rng$ISI[1]`) than 
for the beta-cell function measures (all r<0.30). For correlations
of individual TGFA using mol% with the basic participant characteristics, as shown in 
`r cite_f('heatmap_mol')`, differences in correlations between fatty acids were
most evident for 14:0, 14:1n-7, 16:0, and 16:1n-7 that had a moderate positive
correlation with clinical TG (r=`r fa_cor_mol$rng$TAG[1]`) while all other fatty
acids had a negative association (r=`r fa_cor_mol$rng$TAG[2]`). In particular,
those fatty acids with the negative associations with clinical TG were all the
very long chain polyunsaturated fatty acids (e.g. 20:4n-6, 20:5n-3).
As seen in `r cite_f('heatmap_tagfa')`, four fatty acids (14:0,
16:0, 14:1n-7, and 16:1n-7) clustered together, each highly positively correlated
with each other and negatively correlated with all other fatty acids.
